The Concurrent Calculi Formalisation Benchmark

### 2023-10-11 paper/paper.tex
rework scope extrusion (this time for real)
comment out paragraph in the design

While our challenges require reasoning about binders, which was the main topic of the original POPLMark, they also require other techniques.
Our challenges also require reasoning about logical relations which goes above the reasoning involved in POPLMark Reloaded.\fxwarning{does it? as in do we define a type indexed
  relation and then use that to prove things?}

@@

This is the challenge most closely related to the original POPLMark
challenge since it concerns the properties of binders in restrictions.
It is not clear that the techniques used to solve the POPLMark challenges about binders can be easily extended to reasoning about scope extrusion.
Notably, techniques like Higher Order Abstract Syntax, or well-scoped
De\ Bruijn indices do not have the concept of free variables. For this
kind of system the means to encode the operational semantics are not
obvious.

@@

\subsection{Evaluation criteria}
Solutions to our challenge problems should be compared on three measures: the mechanisation overhead, this being the amount of manually written infrastructure and setup needed to express the definitions in the mechanisation; the adequacy of the formal statements in the mechanisation, i.e.\ whether the proven theorems are easily recognisable as the theorems from the challenge; and the cost of entry for the tools and techniques employed, i.e.\ the difficulty of learning to use the techniques.
Solutions to our challenges do not need to strictly follow the definitions and lemmas set out in the problem text, but solutions which deviate from the original challenges will need to present more elaborate argumentation for their adequacy.

>>>>

% While our challenges require reasoning about binders, which was the main topic of the original POPLMark, they also require other techniques.
% Our challenges also require reasoning about logical relations which goes above the reasoning involved in POPLMark Reloaded.

@@

This is the challenge most closely related to the original POPLMark
challenge since it concerns the properties of binders in restrictions.
It is not clear that the techniques used to solve the POPLMark challenges about binders can be easily extended to reasoning about scope extrusion.
Notably, techniques like Higher Order Abstract Syntax, or well-scoped
De\ Bruijn indices do not have the concept of free variables. It is
not immediately obvious how to encode the operational semantics in
this kind of system.

@@

\subsection{Evaluation criteria}
Solutions to our challenge problems should be compared on three measures: the mechanisation overhead, this being the amount of manually written infrastructure and setup needed to express the definitions in the mechanisation; the adequacy of the formal statements in the mechanisation, i.e.\ whether the proven theorems are easily recognisable as the theorems from the challenge; and the cost of entry for the tools and techniques employed, i.e.\ the difficulty of learning to use the techniques.
Solutions to our challenges do not need to strictly follow the definitions and lemmas set out in the problem text, but solutions which deviate from the original challenges need to present more elaborate argumentation for their adequacy.
